\chapter*{Abstract}

For any patient of food allergies and intolerances, it is vital to know the composition of any food product before consumption. Although the solution is often as trivial as looking at the list of ingredients on the packaging, this task becomes much more complex if the patient is in a foreign country, where they may not know the language or be familiar with the product.

To tackle this problem, this paper proposes the development of a mobile application focused on the case of South Korea. This application incorporates an OCR system that allows the user to recognize the text of the packaging in Korean from the capture of a photograph of the list of ingredients. Combining a pre-built database with translation engines, the application analyzes the identified terms and will alert the user if the product includes any unwanted ingredients.

\par\vskip\baselineskip\noindent
\textbf{Keywords:} Optical character recognition (OCR), ML Kit, Flutter, allergens, Korean language

\chapter*{Resumen}

Para cualquier paciente de alergias e intolerancias alimentarias, es vital conocer la composición de cualquier producto alimenticio antes de su consumo. Aunque la solución suele resultar tan trivial como consultar la lista de ingredientes en el empaquetado, esta tarea se vuelve mucho más compleja si el paciente se encuentra en un país extranjero, donde puede no conocer el idioma ni estar familiarizado con el producto.

Para atajar este problema, en este trabajo se propone el desarrollo de una aplicación móvil enfocada al caso de Corea del Sur. Dicha aplicación incorpora un sistema OCR que permite al usuario reconocer el texto del empaquetado en coreano a partir de la captura de una fotografía de la lista de ingredientes. Combinando una base de datos preconstruida con motores de traducción, la aplicación analiza los términos identificados y alertará al usuario si el producto incluye cualquier ingrediente no deseado.

\par\vskip\baselineskip\noindent
\textbf{Palabras clave:} Reconocimiento óptico de caracteres (OCR), ML Kit, Flutter, alérgenos, idioma coreano